%\section*{User Documentation}
\section{Try Out the Demo}
    Users that want to try the CloudASR demo can do that in Google Chrome web browser.

    \begin{itemize}
	\item Click on the \textbf{Demo} link in the top menu.
	\item Allow the demo to use your microphone.
	\item Select a language that you want to use.
	\item Click on the microphone icon to start recording.
	\item At the end, click on the microphone to stop recording.
	\item
	    During recording, you can switch between the \textbf{Dictation Mode} and the \textbf{Evaluation Mode}.
	    In the Evaluation Mode you can confirm correctness of the transcription or you can add your own transcription.
    \end{itemize}


\section{Transcribe a Recording}
    Users that want to help us by transcribing some of the submitted recordings can do so with the following steps:

    \begin{itemize}
	\item Click on the \textbf{Transcribe} link in the top menu.
	\item Select a language that you want to transcribe and click on the corresponding \textbf{Transcribe} button.
	\item Listen to the recording and add your own transcription.
	\item After you submit your transcription, you can continue with next recording.
    \end{itemize}

\section{Create a CrowdFlower Job}
    Users can also help us by creating a transcription job on CrowdFlower.

    \begin{itemize}
	\item Click on the \textbf{Transcribe} link in the top menu.
	\item Select a language, for which you want create a CrowdFlower job.
	\item Click on the corresponding \textbf{Create CrowdFlower Job} button.
	\item Follow the instructions on that page.
	\item Submit the obtained transcriptions on the \textbf{Upload Results} page.
    \end{itemize}

\section{Select the Best Transcription}
    Administrators can choose the best manual transcription with the following procedure:

    \begin{itemize}
	\item Click on the \textbf{Transcribe} link in the top menu.
	\item Select a language that you want to manage and click on the corresponding \textbf{Recordings} button.
	\item Find a recording, for which you want to select the best manual transcription.
	\item Click on the corresponding \textbf{Transcriptions} button.
	\item Select the best transcription and click on the \textbf{Accept this transcription} button.
    \end{itemize}


\section{Manage Running Workers}
    Administrators can manage labels of the running workers in the following way:

    \begin{itemize}
	\item Click on the \textbf{Transcribe} link in the top menu.
	\item Select a worker that you want to manage and click on the corresponding \textbf{Edit description} button.
	\item
	    Fill in the name and description of the worker.
	    Note that you can use html in the description.
	    You can check your description on a preview at the bottom of the page.
	\item Save the description with the \textbf{Save} button.
    \end{itemize}
